Connecting the Popularity Adjusted Block Model to the Generalized Random Dot Product Graph for Clustering and Parameter Estimation

### 2020-08-19 summary.Rmd
fixed typo

z.hat <- cluster.pabm(A, K)
A.star <- A[order(z.hat), order(z.hat)]
```

For the real data example, we applied Algorithm 2 to the Leeds Butterfly 
dataset \cite{Wang_2018} consisting of visual similarity measurements among 832 
butterflies across 10 species. The graph was modified to match the example 
from \citet{noroozi2019estimation}: Only the 4 most frequent species were 
considered, and the similarities were discretized to $\{0, 1}\$ via 
thresholding. Fig. \ref{fig:butterfly} shows a sorted adjacency matrix sorted 
by the resultant the clustering.

Comparing against the ground truth species labels, Algorithm 2 achieves an 
accuracy of 63\% and an adjusted Rand index of 79\%. In comparison, 
\citet{noroozi2019estimation} achieved an adjusted Rand index of 73\%.

```{r butterfly, fig.height = 5, fig.width = 4, fig.cap = 'Adjacency matrix of the Leeds Butterfly dataset after sorting by the clustering outputted by Algorithm 2.'}
library(plot.matrix)
plot(A.star, border = NA, key = NULL, 
     xlab = '', ylab = '', main = '',
     axis.row = NULL, axis.col = NULL)
```

>>>>

z.hat <- cluster.pabm(A, K)
A.star <- A[order(z.hat), order(z.hat)]

ari <- round(fossil::adj.rand.index(z, z.hat) * 100)
```

For the real data example, we applied Algorithm 2 to the Leeds Butterfly 
dataset \cite{Wang_2018} consisting of visual similarity measurements among 832 
butterflies across 10 species. The graph was modified to match the example 
from \citet{noroozi2019estimation}: Only the 4 most frequent species were 
considered, and the similarities were discretized to $\{0, 1\}$ via 
thresholding. Fig. \ref{fig:butterfly} shows a sorted adjacency matrix sorted 
by the resultant the clustering.

Comparing against the ground truth species labels, Algorithm 2 achieves an 
accuracy of 63\% and an adjusted Rand index of `r ari`\%. In comparison, 
\citet{noroozi2019estimation} achieved an adjusted Rand index of 73\% using 
sparse subspace clustering.

```{r butterfly, fig.height = 3, fig.width = 3, fig.cap = 'Adjacency matrix of the Leeds Butterfly dataset after sorting by the clustering outputted by Algorithm 2.', cache = TRUE}
library(plot.matrix)
plot(A.star, border = NA, key = NULL, 
     xlab = '', ylab = '', main = '',
     axis.row = NULL, axis.col = NULL, asp = 1)
```
